\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage[colorlinks = true,
            linkcolor = red,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\hypersetup{pdfborder = 0 0 0}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\begin{document}

\begin{center}
    {\Huge \scshape Fırtına Küçük} \\ \vspace{1pt}
    {\scshape Teaching Fellow at Mary Immaculate College} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faPhone\ +353 89 492 9528 \& +90 539 343 4946 ~
    \href{mailto:firtina.kucuk@ucd.ie}{\faEnvelope\ firtina.kucuk@ucd.ie} ~ 
    \href{mailto:firtinakucuk@gmail.com}{\faEnvelope\ firtinakucuk@gmail.com} ~ 
    \vspace{-8pt}
\end{center}


% -----------Summary-----------
%\section{Objective}
%  \small{Enter your objective here}
%\vspace{-12pt}
% adjust vscape based on the space you want to leave between each section.


%-----------EDUCATION-----------
\section{Education and Research}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College Dublin, Dublin, Ireland }{September 2019 -- October 2023}
      {Ph.D. in Mathematics}{}
      \resumeItemListStart
        \resumeItem {Passed the viva on 10 July 2023 and the degree is awarded on 20 October 2023.}
        \resumeItem {Supervised by Assoc. Prof. K\^{a}zım Büyükboduk}
        \resumeItem {Thesis Title: Iwasawa Theory of Symmetric Rankin-Selberg Product of Modular Forms and Applications}
    \resumeItemListEnd
      %leave a line after this
      
      %\small{\textbf{Coursework: Course-1, Course-2, Course-3, Course-4}}
      
    \resumeSubheading
      {Koç University, İstanbul, Turkey}{September 2017 -- August 2019}
      {M.Sc. in Mathematics}{GPA: 3.92/4.00}
      %leave a line after this
      \resumeItemListStart
        \resumeItem {Supervised by Prof. Varga Kalantarov}
        \resumeItem {Thesis Title: Global Behaviour of Solutions to Nonlinear Damped Wave Equations}
      \resumeItemListEnd
      %\small{\textbf{Coursework: Course-1, Course-2, Course-3, Course-4}}

      \resumeSubheading
      {Koç University, İstanbul, Turkey}{September 2012 -- June 2017}
      {B.Sc. in Mathematics \& B.Sc. in Computer Engineering (Double Major)}{GPA: 3.33/4.00}
      \resumeItemListStart
      \resumeItem {Senior design project for Computer Engineering, supervised by Prof. Deniz Yüret and Erenay Dayanık}
      \resumeItem {A web interface was built with NodeJS \& React for the VQA (Visual Question Answering) models trained by Erenay Dayanık.}
        \resumeItem {Independent study, supervised by Prof. Varga Kalantarov}
        \resumeItem {The article of H. A. Levine about blow-up of solutions to nonlinear parabolic equations was investigated.}
      \resumeItemListEnd
      \resumeSubheading
      {İstanbul University State Conservatory, İstanbul, Turkey}{2004 -- 2013 \& 2014 -- 2016}
      {Part-Time Piano Department, Advance Level \& Two-year Masterclass}{}

      
  \resumeSubHeadingListEnd
\vspace{-18pt}

\bibliographystyle{utphys}
 \nobibliography*
 \section{Articles and Preprints}
 \begin{enumerate}
  \item \bibentry{kucuk2023factorization} (submitted)
 \end{enumerate}
 \nobibliography{references}

\section{Talks, Summer Schools, Conferences}
  \resumeItemListStart
    \resumeItem {Upcoming Talk: ``Factorization of algebraic $p$-adic Rankin-Selberg $L$-functions'' at ICMAT (Madrid, Spain, November 2024)}
    \resumeItem {Upcoming Talk: ``Factorization of algebraic $p$-adic Rankin-Selberg $L$-functions'' at Mary Immaculate College (Tipperary, Ireland, October 2024)}
    \resumeItem {Talk: ``Factorization of algebraic $p$-adic Rankin-Selberg $L$-functions'' at FGC-HRI-IPM Number Theory Seminars (online, April 2024)}
    \resumeItem{Poster Presentation: "Factorization of Algebraic $p$-adic $L$-functions of Adjoint
    Representations of Coleman Families" at the Conference: Modular Forms, L-functions, and Eigenvarieties (ENS, Paris, June 2024)}
    \resumeItem {Talk: ``Factorization of algebraic $p$-adic Rankin-Selberg $L$-functions'' at FGC-HRI-IPM Number Theory Seminars (online, April 2024)}
    \resumeItem {Talk: ``Factorization of algebraic $p$-adic $L$-functions of Rankin-Selberg products'' at Ottawa/Carleton Number Theory Seminar (online, March 2024)}
    \resumeItem {Talk: ``Factorization of $p$-adic $L$-functions: Towards the $\theta$-critical case'' at UCD Algebra and Number Theory Seminars (November 2023)}
    \resumeItem {Talk: ``Factorization of Algebraic $p$-adic $L$-functions Attached to Adjoint Representations of Coleman Families'' at Koç University (December 2022)}
    \resumeItem {Talk: ``Factorization of Algebraic $p$-adic $L$-functions Attached to Adjoint Representations of Coleman Families'' at UCD Algebra and Number Theory Seminars (March 2022)}
    \resumeItem {Mini Workshop: ``Set Theory and Ordinal Numbers'' at Koç University (December 2016)}
    \resumeItem {Mini Workshop: ``Constructing Numbers: From Natural Numbers to Real Numbers'' at Koç University (March 2017)}
    %\resumeItem {Iwasawa 2023: in memory of John Coates (2023, University of Cambridge, Cambridge/UK, as attendee)}
    %\resumeItem {Explicit methods in automorphic forms and arithmetic geometry (2023, Trinity College Dublin, Dublin/Ireland, as attendee)}
    %\resumeItem {Arithmetic of L-functions (2023, ICMAT, Madrid/Spain, as attendee)}
    %\resumeItem {Introductory Workshop: Algebraic Cycles, L-Values, and Euler Systems (2023, MSRI, Berkeley/CA, as attendee)}
    %\resumeItem {Elliptic Curves and Modular Forms in Arithmetic Geometry (2022, Universit\`{a} degli Studi di Milano, Milan/Italy, as attendee)}
    %\resumeItem {School of Arithmetic Geometry (2022, University of Duisburg-Essen, Essen/Germany, as attendee)}
    %\resumeItem {Arizona Winter School on Modular Forms (2021, Online, as attendee)}
    %\resumeItem {Isaac Newton Institute for Mathematical Science, Swinnerton-Dyer Memorial (2021, Online, as attendee)}
    %\resumeItem {UCD Algebra and Number Theory Seminars (2020-2023, UCD, Dublin/Ireland, as attendee)}
    %\resumeItem {The 31st Journées Arithmétiques (2019, İstanbul University, İstanbul/Turkey, as attendee)}
  %Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
  \resumeItemListEnd
 \vspace{-16pt}

 \section{Non-Academic Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vertigo Games LTD.}{Summer 2016}
      {Intern at Game Development Department}{İstanbul}
      \resumeItemListStart
        \resumeItem {Compulsory internship for Computer Engineering degree (20 workdays)}
        \resumeItem {Tasks: Simple mobile game with Unity Game Engine}
    \resumeItemListEnd
    \resumeSubheading
      {Betek Color Industry Co.}{Summer 2015}
      {Intern at IT Department}{İstanbul}
      \resumeItemListStart
        \resumeItem {Compulsory internship for Computer Engineering degree (20 workdays)}
        \resumeItem {Tasks: Mini projects with SAP’s ABAP programming language}
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-16pt}
\section{Skills and Interests}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Research Interests}{: Algebraic Number Theory, Arithmetic Geometry, Iwasawa Theory} \\
     \textbf{Languages}{: Turkish (mother tongue), English (fluent), German (beginner level)} \\
     \textbf{Computer \& Programming Skills}{: Holding a Double Major Degree in Computer Engineering. GitHub: https://github.com/firtinakucuk. Experience with Python, Javascript, Java, MATLAB, MAGMA Computer Algebra System, LaTeX, C, C\# (Unity), SAP-ABAP. Special interest in Front End Web Development with React \& Backend Development with NodeJS. I built the Koç University-Math204 page for 2018-2019 and 2019-2020 academic year using React: \url{http://home.ku.edu.tr/~math204/} (GitHub link: \url{https://github.com/firtinakucuk/Math204-Webpage})}\\
     \textbf{Music Skills}{: Playing piano since 2002. Graduated from İstanbul University State Conservatory -- Piano Department (Part Time -- Advanced Level) in 2013. Also graduated from two-year masterclass of the same conservatory (2014-2016).}\\
    }}
 \end{itemize}
 \vspace{-16pt}

\section{Teaching Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Mary Immaculate College - Thurles}{August 2024 -- November 2024 (Anticipated)}
      {Teaching Fellow (Lectures \& Tutorials \& Labs)}{Tipperary, Ireland}
      \resumeItemListStart
        \resumeItem {MHP4738 - Computational Mathematics (SageMath, 3 Lectures 1 Tutorial)}
        \resumeItem {MHP4731 - Elementary Number Theory (3 Lectures 1 Tutorial)}
        
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
    \resumeSubheading
      {University College Dublin}{September 2019 -- August 2024}
      {Tutor (Tutorials \& Grading \& Invigilation)}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{MST10030 - Linear Algebra I}
        \resumeItem{MATH10220 - Foundations of Math for Computer Science II}
        \resumeItem{MATH30400 - Further Groups and Rings (I also covered a few lectures)}
        \resumeItem {MATH10240 - Mathematics for Agriculture II (Tutor for 5 consecutive years)}
        \resumeItem {MATH10200 - Matrix Algebra}
        \resumeItem{MATH00010/MST00050 - Introduction to Mathematics/Mathematics: An Introduction (Tutor for 5 consecutive years)} 
        \resumeItem{MATH10310 - Calculus for Science} \resumeItem{MATH10430 - Intro Calculus Engineers(NUin)} 
        \resumeItem{MATH20060 - Calculus of Several Variables}
        \resumeItem{MATH10210 - Foundations of Maths for Computer Science I}
        \resumeItem {MATH10130 - Intro to Analysis for Economics and Finance}
%Based on the number of point you want to add add the "\resumeItem" for each point you want to add.
    \resumeItemListEnd
      
    \resumeSubheading
      {Koç University}{Spring 2017 -- Spring 2019}
      {Teaching Assistant (Problem Sessions \& Grading \& Invigilation)}{İstanbul, Turkey}
      \resumeItemListStart
      \resumeItem{Math 104 - Discrete Mathematics}
      \resumeItem{Math 103 - Introduction to Abstract Mathematics}
      \resumeItem{Math 401 - Complex Analysis (For 2 consecutive years)}
      \resumeItem{Math 204 - Differential Equations (For 2 consecutive years)} 
      \resumeItem{Math 301 - Real Analysis I}  
      \resumeItem{Math 203 - Multivatiable Calculus (During the last semester of my undergraduate)}
    \resumeItemListEnd

    \resumeSubheading
      {Koç University \& Stanford University}{Summer 2017}
      {Section Leader at CS-Bridge Program}{İstanbul, Turkey}
      \resumeItemListStart
        \resumeItem {CS-Bridge was a two-week summer school for programming aimed for high school students. The summer school was co-organized by Koç University and Stanford University (Assoc. Prof. Barış Bozkurt, Prof. Nick McKeown and their colleagues) and it took place at Koç University.}
        \resumeItem {Section leaders held discussion \& lab sessions, provided mentoring to a section of 8 students.}
    \resumeItemListEnd

    \resumeSubheading
      {Koç University Office of Learning and Teaching (KOLT)}{Spring 2017}
      {Tutor at KOLT (individual tutorials)}{İstanbul, Turkey}
      \resumeItemListStart
        \resumeItem{KOLT Tutoring Center provides free individual tutorials to the Koç University students.}
        \resumeItem {Tutored Math 206 (Abstract Algebra II -- Galois Theory) module.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-16pt}
% adjust vscape based on the space you want to leave between each section.


% adjust vscape based on the space you want to leave between each section.


%-----------Technical Skilss-----------

%-----------Technical Skilss-----------



% \section{Projects}
%     \vspace{-6pt}
%     \resumeSubHeadingListStart
%     \resumeProjectHeading
%           {\textbf{Project Title} $|$ \emph{Tool1, Tool2, Tool3, Tool4 \href{https://github.com/}{Git}}}{Month -- Month Year}
%           \resumeItemListStart
%             \resumeItem{ Write about your project experience.}
%             \resumeItem{ Write about your project experience.}
%           \resumeItemListEnd
%           \vspace{-14pt}
%     \resumeProjectHeading
%           {\textbf{Project Title} $|$ \emph{Tool1, Tool2, Tool3, Tool4 \href{https://github.com/}{Git}}}{Month -- Month Year}
%           \resumeItemListStart
%             \resumeItem{ Write about your project experience.}
%             \resumeItem{ Write about your project experience.}
%           \resumeItemListEnd
%           \vspace{-14pt}
%     \resumeProjectHeading
%           {\textbf{Project Title} $|$ \emph{Tool1, Tool2, Tool3, Tool4 \href{https://github.com/}{Git}}}{Month -- Month Year}
%           \resumeItemListStart
%             \resumeItem{ Write about your project experience.}
%             \resumeItem{ Write about your project experience.}
%           \resumeItemListEnd
%           \vspace{-14pt}
%     \resumeProjectHeading
%           {\textbf{Project Title} $|$ \emph{Tool1, Tool2, Tool3, Tool4 \href{https://github.com/}{Git}}}{Month -- Month Year}
%           \resumeItemListStart
%             \resumeItem{ Write about your project experience.}
%             \resumeItem{ Write about your project experience.}
%           \resumeItemListEnd
%           \vspace{-14pt}
%     \resumeSubHeadingListEnd
% \vspace{-3pt}


%------------Publications-----------
% \section{Publication}
% \vspace{-6pt}
%     \resumeSubHeadingListStart
%     \resumeProjectHeading
%     {\textbf{The Title of your paper} $|$ \emph{\href{https://www.researchgate.net}{Publication link}}}{Month Year}
%     \resumeItemListStart
%             \resumeItem{Write about your paper.}
%             \resumeItem{Write about your paper.}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd
% \vspace{-16pt}
% adjust vscape based on the space you want to leave between each section.


\section{Honors and Awards}
\textbf{Vehbi Koç High Honors Award} {: Awarded for attaining an outstanding academic performance and GPA/SPA over 3.50 (2014, 2015, 2017)}\\
\textbf{Bronze Medal in National Mathematics Olympiads in Turkey} {(2011)}\\
\textbf{Silver Medal in Antalya Mathematics Olympiads} {(2011)}\\
\textbf{MEB İstanbul Science Olympiads Bronze Medal} {(2011)}\\
\textbf{Sabancı University Mathematics Competition 3rd prize} {(2011)}\\
\textbf{Bilgi University Cahit Arf Mathematics Days Honorable mention} {(2010)}


\section{Scholarships}
\textbf{UCD Ph.D. Advance Core Scheme} {2019-2023} \\
\textbf{TUBITAK – Bideb 2210} {: Given during the master’s study, as a continuation of Bideb 2205 (2017-2019)}\\
\textbf{TUBITAK – Bideb 2205} {: Given to the science major students who was in top 5000 nationwide in the university entrance exams (2012-2017)}\\
\textbf{TEV (Turkish Education Foundation) High Success Scholarship} {(2012-2017)}\\
\textbf{Koç University Semahat Arsel Scholarship} {: Given to the students who entered Koç University in the top 30 (2012-2017)}

% \section{References}
% \resumeSubHeadingListStart
%   \resumeSubheading
%       {Kâzım Büyükboduk}{University College Dublin}
%       {kazim.buyukboduk@ucd.ie}{}
%   \resumeSubheading
%       {Antonio Lei}{University of Ottawa}
%       {alantoniolei@gmail.com}{}
%   \resumeSubheading
%       {Matteo Longo}{Universita di Padova}
%       {mlongo@math.unipd.it}{matteo.longo@unipd.it}
% \resumeSubHeadingListEnd
\end{document}